### 2023-11-04 main.tex
ll

By knowing the steady state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the steady state of the Hamiltonian $H^{'}$. The result is the following 

@@

For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis} we have
	\Psi^{''}(\bm{\mu})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\co

@@

\subsection{Explicit formula for the steady state $|\Psi\rangle$}

>>>>

By knowing the ground state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the ground state of the Hamiltonian $H^{'}$. The result is the following 

@@

{\color{blue}$\mu$ or $\tau$ here?}

For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis} we have
\begin{equation}
	\Psi^{''}(\bm{\mu})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
\end{equation}
\begin{comment}
\begin{equation}
	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\co
\end{equation}
\end{comment}
 \begin{comment}

@@

\subsection{Explicit formula for the steady state $|\Psi\rangle$}
{\color{blue}can we proceed as above? using sth similar to \eqref{goodTP-S2}}
